Determining the alternatives for scalar implicature

### 2016-01-24 Paper/Paper.tex
relative plots
mcf pass 1

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{float}

@@

\title{The importance of alternatives in scalar implicature}

@@

\begin{abstract}
Succesful communication regularly requires listeners to make pragmatic
inferences - enrichments beyond the literal meaning of a speaker's
utterance. For example, listeners routinely enrich the meaning of
``some'' to ``some, but not all'' when interpreting a sentence such as
``Bob ate some of the cookies.'' A Gricean account of this phenomena
assumes the presence of \emph{salient alternatives} with varying degrees
of informativity. ``Some,'' in the example above, is enriched to ``some,
but not all'' in the presence of the stronger alternative ``all.''
Empirical evidence for the presence of such alternatives and accounts of
their effect on implicature has been limited. Our current work explores
the role different scale representations may play in scalar implicature
using empirical measures of literal semantics and a Bayesian model of
implicature generation. Comparisons with human judgments indicate that
pragmatic inference may rely on fairly complete alternative sets rather
than the typical entialment only scales assumed in most research to
date.

@@

Humpty Dumpty Quote\ldots{}

Successful communication regularly requires listeners to make inferences
that go beyond the literal semantic content of a speaker's utterance.
``Scalar implicature'' is a hallmark of such pragmatic enrichment. For
example, listeners routinely enrich the meaning of the scalar item
``some'' to ``some, but not all'' in sentences like ``Bob ate some of
the cookies'' (van Tiel, 2014; other\ldots{}). A Gricean account of this
phenomena assumes listeners reason about the intended meaning of a
speaker while incorporating knowledge about a) alternative scalar items
a speaker could have used (such as ``all'') and b) the relative
informativity of using such alternatives (Grice, 1975). Under the
Gricean account, a listener will infer that the speaker must have
intended that Bob did not eat ``all'' the cookies because it would have
been \emph{underinformative} for the speaker to use ``some'' when
``all'' could have been used.

The presence of ``salient" alternatives is critical to the standard
Gricean account of scalar implicature (Grice, 1975). Recent experimental
evidence appears to support this. Using a gumball paradigm, Degen \&
Tanenhaus (2014) demonstrated that the scalar item \emph{some} was
judged less appropriate (natural) for small sets of items when exact
numbers were seen as viable alternatives. This finding points to the
impact a particular alternative set can have on judgments regarding
scalar appropriateness. Using a fundamentally different approach, Franke
(2014) formalized the Gricean account of implicature using a Bayesian
model, modeling graded typicality judgments and scalar implicature.
Results supported `none', `one' and `all' as the most serious (salient)
alternatives to ``some.''

Taken together, each of the previous studies signal the importance of
scale representation (set of available alternatives) in scalar
implicature. However, like many recent investigations which have focused
only on a small subset of scalar items, both Degen \& Tanenhaus (2014)
and Franke (2014) focus exclusively on the scalar family ``some/all.''
This lack ``Scalar Diversity'' (van Tiel, 2014) makes generalization
across different scalar families problematic. van Tiel (2014), found
substantial variation in the rate of upper-bounded construals aross more
than 40 different scalar pairs. This finding suggests that implicature
may differ widely between different scales. We adopt a ``Scalar
Diversity'' approach in our experimental design in order to extend our
investigation beyond ``some/all'' scalar items. In the following set of
studies we examine implicature for ``some/all'' and five additional
scalar families from a range of grammatical classes (see Figure 5 for a
complete set of scalar items used). The set of scalar items for this
study were chosen from among the 40 used in van Tiel (2014).

Consider a scalar item other than ``some'' - in the context of the word
``good'', the idea of set of lexical alternatives seems intuitive
(``bad'', ``excellent'', etc.). But measuring the extent to which these
alternatives are salient is not so clear. Nor is how to measure their
impact on pragmatic interpretations of the scalar item ``good.'' In an
experimental setting, querying a participant about the saliency of a
particular alternative is problematic because the alternative must be
made salient during the query. In the spirit of Franke (2014) and Degen
\& Tanenhaus (2014), we pair a computational model of implicature with
empirical measurements of linguistic material. This combination allows
us to simulate the effect of various scale representations on
implicature. In particular, we adopt a Bayesian model of implicature and
a food-review paradigm to empirically quantify literal semantics and
pragmatic judgments for our scalar stimuli.

Bayesian models of pragmatic enrichment have accurately predicted human
judgments in ad-hoc (Frank \& Goodman, 2012) and embedded (Stulhmuller
\& Goodman, 2014) implicature settings. Our current model follows both
these studies and is based on Rational Speech-act theory (RSA). RSA
frames language understanding as a special case of social cognition
(Frank \& Goodman, 2012; Stulhmuller \& Goodman, 2014), in which
listeners and speakers reason about one-another. In this framework, a
listener uses Bayesian inference to interpret the intended meaning \(m\)
of a speaker who has made an utterance \(u\). We will make the model
specifications explicit later in the paper.

In the following study we investigate the role of scale representation
on scalar implicature. To do so we combine a computational framework
with empirical measurements to simulate the type of scale
representations that might be available to a listener. In the following
sections we outline the specifics of the model and the particular
components for which we need to to make empirical measurements. We then
outline a series of experiments meant to a) quantify literal semantics
for otherwise ambiguous scalar items, b) measure pragmatic judgments and
c) generate a set of plausible alternatives for our set of scalar pairs
taken from van Tiel (2014). In particular, we adopt a food review
paradigm throughout our empirical data gathering, quantifying linguistic
meaning (both literal semantics and pragmatic judgments) as
distributions over star ratings. Finally, we simulate the impact of
three different scale representations, ``entailment'', ``mid'' and
``symmetric'' on implicature generation, comparing model predictions
with pragmatic judgments captured empirically. Results indicate that
humans may employ more ``fully specified'' scale representations,
relying on the presence of multiple alternatives during pragmatic
enrichment.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\section{Modeling implicature: Rational Speech-act
theory}\label{modeling-implicature-rational-speech-act-theory}

We adopt a Bayesian model of scalar implicature known as Rational
Speech-act theory (RSA). In particular, RSA frames language
understanding as a special case of social cognition (Frank \& Goodman,
2012; Stuhmuller \& Goodman, 2014) in which listener and speaker agents
reason about one another. We focus on the problem of a listener
inferring the meaning of a speaker's utterance. Let \(u\) be an observed
utterance made by our speaker with an intended meaning \(m\). We assume
that the listener has access to a space of possible meanings \(M\) and
some model relating meanings \(m \in M\) to \(u\).

Upon hearing an utterance \(u\) the Listener agent evaluates all
candidate word meanings, computing their posterior probabilities
\(p_{L1}(m | u)\). This quantity is proportional to the product of the
prior probability \(p(m)\) of a particular meaning and the likelihood
\(p(u | m)\).

\[p_{L1}(m | u) = \frac{p(u | m)p(m)}{p(u)}\]
\[= \frac{p(u | m)p(m)}{\sum_{m \in M}p(u | m)}\]

The \textbf{prior} \(\mathbf{p(m)}\) represents the listener's
expectations about plausible meanings (star ratings), \emph{independent}
of the utterance \(u\). To avoid biasing the data we assume priors over
meanings are uniform, however future investigations may want to
experiment with different priors, either by inferring them or using
empirical measures

\(\mathbf{p(u | m)}\) quantifies the \textbf{likelihood} that a speaker
would make a particular utterance \(u\) given an intended meaning \(m\).
Our model assumes that speakers choose words to maximize the utility of
an utterance in context. Utility is operationalized as the informativity
of a particular utterance (surprisal) minus a cost. In particular, the
speaker chooses an utterance in order to maximize the utility of a
listener who interprets her utterance literally \(p_{L0}(m|u)\). \(L_0\)
denotes a literal listener interpretation of meaning \(m\) given
utterance \(u\).
\[p(u | m) = \frac{e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}\]

The \textbf{posterior} \(\mathbf{p_{L1}(m | u)}\) quantifies a
listener's degree of belief that a speaker intended a meaning \(m\)
given an utterance \(u\). The subscript \(L_1\) denotes a pragmatic
listener interpretation of meaning \(m\) given utterance \(u\).

\subsection{Simluating implicature: Measuring literal semantics and
pragmatic
judgments}\label{simluating-implicature-measuring-literal-semantics-and-pragmatic-judgments}

In order to simulate the role of scale representation on implicature we
pair a computational framework with empirical data. In particular we use
experimental tools to populate three components of the model. First, to
measure otherwise ambiguous literal semantics \(\mathbf{p_{L0}(m|u)}\)
(our ``Scalar Diversity''" approach). Second, to generate a set of
plausible alternatives to the original scalar pairs taken from van Tiel
(2014). Lastly, to obtain human pragmatic judgments for model comparison
\(\mathbf{p_{L1}(m|u)}\).

Starting with the first component, consider the scalar items ``some''
and ``all.'' Both are convenient for modeling in a computational
framework like the one we've proposed above. Their literal semantics
\(\mathbf{p_{L0}}\) are easily quantified over sets.

\[\text{\text it{some of the A's are B's.}}\]
\[[[some]] = \{<A, B> : |A \cap B| \geq 1 \}\]

\[\text{\text it{all of the A's are B's.}}\]
\[[[all]] = \{<A, B> : \frac{|A \cap B|}{|A|} == 1 \}\]

The same cannot be said for items such as ``good / excellent'',
``memorable / unforgettable'' or ``liked / loved.''

In the following set of studies we adopt a food-review paradigm to
measure literal semantics and pragmatic judgments empirically. In order
to capture graded typicality judgments as in Degen \& Tanenhaus (2014)
we use a compatibility measure dependent variable, pairing scalar items
with star-ratings in our literal listener task (Experiments 1a, 3a and
4). Data from these experiments is used to approximate the literal
listener semantics for a given scalar item \(u\) as a distribution over
star-ratings \(m \in \text{\{1 - 5 stars\}}\). Similarly, pragmatic
judgment data from Experiments 1b and 3b serve as our primary points of
comparison with model predictions \(\mathbf{p_{L1}(m|u)}\), again
quantifying judgments as distributions over star-ratings. In the
following section we take the reader through our experiments.

\begin{CodeChunk}
\begin{figure*}[t]

@@

\caption[The left panel shows a trial from Experiment 1a with the target scalar `liked']{The left panel shows a trial from Experiment 1a with the target scalar `liked'. Participants responses to the binary dependent variable are used to quantify literal semantics. The right panel shows a trial from Experiment 1b with the target scalar `liked'. Participants were asked to generate the star rating they think the speaker likely intended, given the target scalar (in this case 'liked').}\label{fig:stimuli_exp1}
\end{figure*}
\end{CodeChunk}

Experiment 1a and 1b were conducted to approximate literal listener
semantic distributions \(p_{L0}(m|u)\) (Experiment 1a) and pragmatic
judgments \(p_{L1}(m|u)\) (Experiment 1b) for five pairs of scalar items
taken from van Tiel (2014) (see figure 5 for stimuli). Each pair
consists of a ``weaker'' scalar term (e.g. ``some'') and a stronger
scalar term (e.g. ``all''). We are calling these ``entailment scales'',
because they encode the assumption that a listener need only have a the
stronger alternative present to generate an enriched interpretation of
the weaker term. The grey colored items in Table 1 denote the original
``entailment'' items used in Experiments 1a,b.

@@

Participants for both tasks were recruited on Amazon Mechanical Turk and
paid \$0.20 for their participation. Thirty participants were recruited
for Experiment 1a. Data for two participants was thrown out during
analysis because they were not native English speakers, leaving a total
sample of 28 participants. Fifty participants were recruited for
Experiment 1b. Data for 7 participants was thrown out after participants
either failed to pass two training trials or were not native English
speakers, leaving a total sample of 43 participants.

@@

The left panel of Figure 1 shows a screen shot of a trial from
Experiment 1a. Participants were presented with a target scalar item and
a star-rating (between 1-5 stars) and asked to judge the compatibility
of the scalar item and star-rating. Compatibility was assessed through a
binary ``yes/no'' response to a question of the form ``Do you think that
the person thought the food was \_\_\_\_?" where a target scalar was
presented in the ``\_\_\_\_." Each participant was presented all scalar
item and star-rating combinations with randomization.

The right panel of Figure 1 shows a screen shot of a trial from
Experiment 1b. On each trial, participants were presented with a
one-sentence prompt containing a target scalar item such as ``Someone
said they thought the food was \_\_\_\_\_.'' Participants were then
asked to generate a star-rating according to what they thought the
reviewer likely gave. Each participant was presented all scalar items
with randomization.

@@

\begin{CodeChunk}
\begin{figure*}[t]

@@

\caption[The left panel plots literal semantic distributions for the scalar pair 'liked/loved']{The left panel plots literal semantic distributions for the scalar pair 'liked/loved'. The y-axis is the percentage of 'yes' responses for a scalar term that is compatibible with the number of stars on the x-axis (ie 100\% of respondents beleived that 'liked' was compatible with both 4 and 5 stars). Erro bars are 95\% confidence intervals. The right panel plots pragmatic judgments for the scalar pair 'liked/loved'. The y-axis is the proportion of selection of the star-rating on the x-axis (ie over 80\% of judgments when prompted with 'loved' were 5-stars).}\label{fig:exp1Plots}
\end{figure*}
\end{CodeChunk}

@@

\textbackslash{}begin\{CodeChunk\}
\textbackslash{}begin\{figure\}{[}h{]}

\{\centering \includegraphics{figs/allScalesTable-1}

\}

\textbackslash{}caption{[}This table shows the stimuli used in
Experiments 1a,b, 3a,b and 4{]}\{This table shows the stimuli used in
Experiments 1a,b, 3a,b and 4. Colors denote the additions made in each
experiment. For example, in Experiment 1a we measured literal semantics
for `liked/loved'. In Experiment 3a,b we extended this group to
`textit\{hated/disliked/liked/loved'. In Experiment 4 we extended this
grou to `hated/disliked/felt indifferent
about/liked/loved'.\}\label{fig:allScalesTable}
\textbackslash{}end\{figure\} \textbackslash{}end\{CodeChunk\}

@@

Ignore below this

use a food review paradigm in which `meaning' for a given scalar item
was quantified as a distribution over star-ratings. Quantifying both
literal semantic content and pragmatic judgments as distributions over
stars provides an important interface to our model, especially for
scalar items with ambiguous literal semantics (e.g.~items such as
``liked/loved'' or ``memorable/unforgettable''). In addition to
quantifying literal semantics and pragmatic judgments in Experiments
1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task,
based on van Tiel (2013, Experiment 2???), to generate a set of
plausible alternatives to the scalar items used in Experiments 1a,b. We
extend the set of alternatives measured in Experiments 3a,b and 4 using
data from Experiment 2. Additionally, by looking at the relative
frequencies of alternatives generated in Experiment 2 we were able to
compute a saliency measure for each alternative. Using the literal
semantic data from Experiments 1a, 3a and 4, we modeled pragmatic
enrichment using RSA and compared model predictions to human judgments
obtained in Experiments 1b and 3b. Model performance was significantly
improved with the incorporation of alternatives. This result suggests
that more ``fully specified" scale representations may be active for
human participants while making pragmatic judgments for scalar items.

>>>>

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{float}
\usepackage{caption}

@@

\title{Determining the alternatives for scalar implicature}

@@

\begin{abstract}
Succesful communication regularly requires listeners to make pragmatic
inferences - enrichments beyond the literal meaning of a speaker's
utterance. For example, when interpreting a sentence such as ``Bob ate
some of the cookies,'' listeners routinely infer that Bob did not eat
all of them. A Gricean account of this phenomena assumes the presence of
alternatives (like ``all of the cookies'') with varying degrees of
informativity, but it remains an open question precisely what these
alternatives are. We use a computational model of pragmatic inference to
test out hypotheses about how well different sets of alternatives allow
us to predict scalar implicature performance across a range of different
scales. Our findings suggest that human comprehenders likely consider a
much broader set of alternatives beyond those entailed by the initial
description.

@@

Successful communication requires listeners to make pragmatic inferences
that go beyond the literal semantic content of speakers' utterances. For
example, listeners commonly enrich the meaning of the scalar item
``some'' to ``some but not all'' in sentences like ``Bob ate some of the
cookies'' (Grice, 1975; Horn, 1984; Levinson, 2000). These inferences,
called \emph{scalar implicatures}, have been an important test case for
understnading pragmatic inferences more generally. A Gricean account of
this phenomena assumes listeners reason about the meaning the speaker
intended by incorporating knowledge about a) alternative scalar items a
speaker could have used (such as ``all'') and b) the relative
informativity of using such alternatives (Grice, 1975). According to
this account, a listener will infer that the speaker must have intended
that Bob did not eat ``all'' the cookies because it would have been
\emph{underinformative} for the speaker to use ``some'' when ``all''
could have been used.

But what are the alternatives that should be considered in this
computation more generally? Under classic accounts of implicature,
listeners consider only those words whose meaning would entail the word
that is actually sent (Horn, 1972), and these alternatives enter into
conventionalized or semi-conventionalized scales (Levinson, 2000). For
example, because ``all'' entails ``some,'' and hence is a ``stronger''
meaning, ``all'' should be considered as an alternative to ``some'' in
implicatures. Similar scales exist for non-quantifier scales, e.g.
``love'' entails ``like'' (and hence ``I liked the movie'' implicates
that I didn't love it).

Recent empirical evidence has called into question whether entailment
scales are all that is necessary for understanding scalar implicature.
For example, Degen \& Tanenhaus (2015) demonstrated that the scalar item
``some'' was judged less appropriate when exact numbers were seen as
viable alternatives. And in a different paradigm, Tiel (2014) found
converging evidence that ``some'' was judged to be atypical for small
quantities. These data provide indirect evidence about a broader set of
alternatives: since ``some'' is logically true of sets with one or two
members, these authors argued that the presence of salient alternatives
(the words ``one'' and ``two'') reduced the felicity of ``some'' via a
pragmatic inference.

By formalizing pragmatic reasoning, computational models can help
provide more direct evidence about the role that alternatives play. The
``rational speech act'' model (RSA) is one recent framework for
understanding inferences about meaning in context (Frank \& Goodman,
2012; N. D. Goodman \& Stuhlm{ü}ller, 2013). RSA models frame language
understanding as a special case of social cognition, in which listeners
and speakers reason recursively about one another's goals. In the case
of scalar implicature, a listener makes a probabilistic inference about
what the speaker's most likely communicative goal was, given that she
picked the quantifier ``some'' rather than the stronger quantifier
``all.'' In turn, the speaker reasons about what message would best
convey her intended meaning to the listener, given that he is reasoning
in this way. This recursion is grounded in a ``literal'' listener who
reasons only according to the basic truth-functional semantics of the
language.

Franke (2014) used an RSA-style model to assess what alternatives a
speaker would need to consider in order to produce the
typicality/felicity ratings reported by Degen \& Tanenhaus (2015) and
Tiel (2014). In order to do this, Franke (2014)'s model assigned weights
to a set of alternative numerical expressions. Surprisingly, along with
weighting ``one'' highly (a conclusion that was suppored by the
empirical work),the best-fitting model assigned substantial weight to
``none'' as an alternative. This finding was especially surprising
considering the emphasis of standard theories on scalar items that stand
in entailment relationships with one another (e.g. ``one'' entails
``some'' even if it is not classically considered to be part of the
scale scale).

In our current work, we pick up where these previous studies left off,
considering the set of alternatives for implicature using the RSA model.
To gain empirical traction on this issue, however, we broaden the set of
scales we consider. Our inspiration for this move comes from work by Van
Tiel, Van Miltenburg, Zevakhina, \& Geurts (2014), who examined a
phenomenon that they dubbed ``scalar diversity,'' namely the substantial
difference in the strength of scalar implicature across a variety of
scalar pairs (e.g. ``liked/loved,'' or ``palatable/delicious.''). Making
use of some of this diversity allows us to investigate the ways that
different alternative sets give rise to implicatures of different
strengths across scales.

We begin by presenting the computational framework we use throughout the
paper. We next describe a series of experiments deisgned to measure both
the literal semantics of a set of scalar items and comprehenders'
pragmatic judgments for these same items. These experiments allow us to
compare the effects of different alternative sets on our ability to
model listeners' pragmatic judgements. To preview our results: we find
that standard entailment alternatives do not allow us to fit
participants' judgements, but that expanding the range of alternatives
empirically (by asking participants to generate alternative messages)
allows us to model listener judgements with high accuracy.

\section{Modeling Implicature Using
RSA}\label{modeling-implicature-using-rsa}

We begin by giving a brief presentation of the basic RSA model. This
model simulates the judgements of a pragmatic listener who wants to
infer a speaker's intended meaning \(m\) from her utterance \(u\). For
simplicity, we present a version of this model in which there is only
full recursion: that is, the pragmatic listener reasons about a
pragmatic speaker, who in turn reasons about a ``literal listener.'' We
assume throughout that this computation takes place in a signaling game
(Lewis, 1969) with a fixed set of possible meanings \(m \in M\) and a
fixed possible set of utterances \(u \in U\), with both known to both
participants. Our goal in this study is to determine what utterances
fall in \(U\).

In the standard RSA model, the pragmatic listener (denoted \(L_1\)),
makes a Bayesian inference:

\[p_{L1}(m \mid u) \propto p_{S_1} (u \mid m) p(m)\]

\noindent In other words, the probability of a particular meaning given
an utterance is proportional to the speaker's proability of using that
particular utterance to express that meaning, weighted by a prior over
meanings. This prior represents the listener's \emph{a priori}
expectations about plausible meanings, independent of the utterance.
Because our experiments take place in a context in which listeners
should have very little expectation about which meanings speakers want
to convey, for simplicity we assume a uniform prior \(p(m) \propto 1\).

The pragmatic speaker in turn considers the probability that a literal
listener would interpret her utterance correctly:

\[ p_{S_1} (u \mid m) \propto p_{L_0} (m \mid u)\]

\noindent where \(L_0\) refers to a listener who only considers the
truth-functional semantics of the utterance (that is, which meanings the
utterance can refer to).

This model of the pragmatic speaker is consistent with a speaker who
choses words to maximize the utility of an utterance in context (Frank
\& Goodman, 2012), where utility is operationalized as the informativity
of a particular utterance (surprisal) minus a cost:

\[p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))},\]

\noindent where \(C(u)\) is the cost of a particular utterance,
\(-log(p_{L_0})\) represents the \emph{surprisal} for the literal
listener (the information content of the utterance), and (\(\alpha\) is
a parameter in a standard choice rule. If \(\alpha=0\), speakers choose
randomly and as \(\alpha \rightarrow \infty\), they greedily choose the
highest probability alternative. In our simulations below, we treat
\(\alpha\) as a free parameter and fit it to the data.

To instantiate our signaling game with a tractable message set \(M\), in
our studies we adopt a food-review paradigm: we assume that speakers and
listeners are trying to communicate the number of stars in an onine
restaurant review (where \(m \in \{1, 2, 3, 4, 5\}\)). We then use
experiments to measure three components of the model. First, to measure
literal semantics \({p_{L_0} (m \mid u)}\) (we ask experiment
participants to judge whether a message is applicable to a particular
meaning (Experiments 1a, 3a, and 4). Second, to generate a set of
plausible alternative messages in \(U\), we elicit alternatives directly
(Experiment 2). Lastly, to obtain human \(L_1\) pragmatic judgments, we
ask participants to interpret a speaker's utterances.

\begin{CodeChunk}
\begin{figure}[t]
\includegraphics{figs/allScalesTable-1} \caption[Stimuli for Experiments 1a,b, 3a,b and 4]{Stimuli for Experiments 1a,b, 3a,b and 4.}\label{fig:allScalesTable}
\end{figure}
\end{CodeChunk}

\begin{CodeChunk}
\captionsetup{width=0.8\textwidth}\begin{figure*}[t]

@@

\caption[(Left) A trial from Experiment 1a (literal listener) with the target scalar `liked]{(Left) A trial from Experiment 1a (literal listener) with the target scalar `liked.' (Right) A trial from Experiment 1b (pragmatic listener) with the target scalar `liked.'}\label{fig:stimuli_exp1}
\end{figure*}
\end{CodeChunk}

Experiment 1a and 1b were conducted to approximate literal listener
semantic distributions \(p_{L_0}(m \mid u)\) (Experiment 1a) and
pragmatic judgments \(p_{L_1}(m \mid u)\) (Experiment 1b) for five pairs
of scalar items taken from Tiel (2014). Scales and alternative
utterances are shown in Figure \ref{fig:allScalesTable}. Each pair of
scalar items consists of a ``weaker'' term (e.g. ``some'') and a
stronger term (e.g. ``all''). We begin with these classic members of the
Horn scale (Horn, 1972) as a test of the hypothesis that these
alternatives are all that is necessary to predict the strength of
listeners' pragmatic inferences.

@@

We recruited 30 participants from Amazon Mechanical Turk (AMT) for
Experiment 1a; two participants were excluded because they reported
having a native language other than English for a final sample of 28
participants. We recruited 50 for Experiment 1b, also from AMT, and data
for 7 participants were excluded after participants either failed to
pass two training trials or reported a non-English native language,
leaving a total sample of 43 participants.

@@

Figure \ref{fig:stimuli_exp1} shows the experimental setup for both
experiments. In Experiment 1a, the literal listener task, participants
were presented with a target scalar item and a star rating (1--5 stars)
and asked to judge the compatibility of the scalar item and star-rating.
Compatibility was assessed through a binary ``yes/no'' response to a
question of the form ``Do you think that the person thought the food was
\_\_\_\_?" where a target scalar was presented in the blank. Each
participant saw all scalar item and star rating combinations, in a
random oder.

In Experiment 1b, the pragmatic listener experiment, participants were
presented with a one-sentence prompt containing a target scalar item
such as ``Someone said they thought the food was \_\_\_\_\_.''
Participants were then asked to generate a star rating representing the
rating they thought the reviewer likely gave. Each participant was
presented with all scalar items in a random order.

@@

\begin{CodeChunk}
\captionsetup{width=0.8\textwidth}\begin{figure*}[t]

@@

\caption[Literal listener judgements from Experiments 1a, 3a, and 4]{Literal listener judgements from Experiments 1a, 3a, and 4. Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).  Each panel shows one scalar pair.}\label{fig:exp1Plots}
\end{figure*}
\end{CodeChunk}

@@

@@

Degen, J., \& Tanenhaus, M. K. (2015). Processing scalar implicature: A
constraint-based approach. \emph{Cognitive Science}, \emph{39}(4),
667--710.

Frank, M., \& Goodman, N. (2012). Predicting pragmatic reasoning in
language games. \emph{Science}, \emph{336}(6084), 998.

Franke, M. (2014). Typical use of quantifiers: A probabilistic speaker
model. In \emph{Proceedings of the 36th annual conference of the
cognitive science society} (pp. 487--492).

Goodman, N. D., \& Stuhlm{ü}ller, A. (2013). Knowledge and implicature:
Modeling language understanding as social cognition. \emph{Topics in
Cognitive Science}, \emph{5}(1), 173--184.

Grice, H. P. (1975). Logic and conversation. In P. Cole \& J. Morgan
(Eds.), \emph{Syntax and semantics} (Vol. 3). New York: Academic Press.

Horn, L. R. (1972). \emph{On the semantic properties of logical
operators.} (PhD thesis). University of California, Los Angeles.

Horn, L. R. (1984). Toward a new taxonomy for pragmatic inference:
Q-based and R-based implicature. \emph{Meaning, Form, and Use in
Context}, \emph{42}.

Levinson, S. C. (2000). \emph{Presumptive meanings: The theory of
generalized conversational implicature}. MIT Press.

Lewis, D. (1969). \emph{Convention: A philosophical study}. John Wiley
\& Sons.

Tiel, B. van. (2014). Quantity matters: Implicatures, typicality, and
truth.

Van Tiel, B., Van Miltenburg, E., Zevakhina, N., \& Geurts, B. (2014).
Scalar diversity. \emph{Journal of Semantics}, ffu017.
